Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-16 Manuscript/Manuscript.tex
Small edits

\begin{abstract}
Valuation effects are consistently observed in medial prefrontal and
posterior cingulate cortex (mPFC and PCC). The spatial extent of these
effects is mostly indistinguishable from the default mode network (DMN)
in existing meta-analyses. However, little is known about how valuation
effects fit within the broader functional architecture of mPFC and PCC,
or whether that architecture is consistent or idiosyncratic across
individuals. Here we complement a meta-analysis with fMRI-based graph
theoretic approaches to subdivide mPFC and PCC at the single-subject
level. Our results suggest the functional topography of mPFC has
substantial variability across individuals. This highlights the
potential usefulness of estimating brain effects at the individual level
in this region, and points to limitations of aggregative methods such as
coordinate-based meta-analysis in determining whether valuation and DMN
effects emerge from common or separable brain systems. Our approach
shows promise in addressing this issue through future manipulations of
valuation.
\end{abstract}

@@

One of the main goals of human cognitive neuroscience is to be able to
prescribe function to brain regions, either in isolation or in their
communication with others. Among general regions of the brain, the
medial prefrontal cortex (mPFC, located in the midline frontal portion
of the brain) has been suggested to subserve the cognitive abilities
that differentiate humans from other animals (Barbas \& Garcia-Cabezas,
2016). Specifically, this region has been related to a variety of
functions, including decision making (Bartra, McGuire, \& Kable, 2013),
memory encoding (Shacter, Addis, \& Buckner, 2007), and default mode
deactivation (DMN) (Yeo et al., 2011). While much has been discovered
about this area in primates (Barbas \& Garcia-Cabezas, 2016), the lack
of direct measurements of neuronal activity makes this a tough area to
record in humans, one that nowadays relies mostly on functional MRI
(fMRI). Unfortunately, the mPFC is especially challenging to image, as
the oxygen-related signal recorded by fMRI is contaminated by the oxygen
in the sinuses (Logothetis, 2008). In addition, this area is subject to
more idiosyncratic cortical folding than any other region (Zilles,
Palomero- Gallagher, \& Amunts, 2013), thus adding a level of complexity
to the generalizable dissection of topographic functional roles within
mPFC.

Studies of valuation have consistently shown functional overlap with
DMN. Recent meta-analytic work has attempted to distinguish the brain
areas belonging to each by examining the locus of peak activity across
studies related to the behavioral features mentioned above (Bartra et
al., 2013; Acikalin, Gorgolewski, \& Poldrack, 2017). While this
approach offers valuable information, it is subject to the quality of
imaging in each study, as well as their corresponding differences in
tasks used to examine choice. In addition, recent findings suggest that
the functional topology of the brain is better understood by accounting
for organizational idosyncrasies (Braga and Buckner, 2018; Yeo et al.,
2018, Gordon et al., 2017, Gratton\ldots{}).

Given the shortcomings of study-specific and cross-study analyses
mentioned above, there is potential value in combining complementary
strengths from both approaches. While my lab is primarily interested in
the portion of mPFC dedicated to decision making, in order to bypass the
heterogeneity in behavioral tasks, it might be best to disentangle the
mPFC by focusing first on which of its sub-regions belong to
resting-state DMN, and which do not. The advantage lies in that (1) all
resting state scans are performed equally (the subject lies in the
scanner with their eyes open), and (2) there is a high quality resource
of resting state data provided by the Human Connectome Project. Focusing
on resting state data has been successful in determining a number of
neural phenomena, including disentangling auditory and visual attention
areas (Tobyne, Osher, Michalka, \& Somers, 2017).

This approach opens an opportunity to examine brain dynamics. For
example, a region's function might depend on its connectivity at any
given time with one brain community or another. An ever-growing trend in
human neuroimaging has been to apply network statistics to tackle these
functional challenges. One great advantage of network science is the
ability to characterize connectivity in a way that allows for
comparisons among individuals in a meaningful way (Garcia, Ashourvan,
Muldoon, Vettel, \& Bassett, 2018), thus letting us address the folding
idiosyncrasies mentioned above. Therefore, I propose to use some of the
statistics that we have learned in class to estimate intrinsic
functional subdivisions of the mPFC at the individual subject level.
Particularly, I would like to distinguish communities related to DMN
from non-DMN, so that we can generate more informed topographic targets
for future studies of decision making.

In this study, I try to address my question at 3 levels of granularity:
1) across the literature (meta-analysis), selecting a number of regions
of interest (ROI) that show significant overlap and specificity between
DMN and decision making; 2) full-brain connectivity of actual fMRI data,
using a pre-specified brain atlas; and 3) characterizing the
connectivity of surface vertices (small units of function that contain
oxygen-dependent neural information across time) for the regions
selected in step one. I performed the last two steps at an individual
subject level for 3 subjects, hoping to find some commonalities among
them. In this way, I attempted to extract functional topographical
information from topological network features.

@@

@@

@@

\section*{Results}\label{results-1}
\addcontentsline{toc}{section}{Results}

Please note that whilst this template provides a preview of the typeset
manuscript for submission, to help in this preparation, it will not
necessarily be the final publication layout. For more detailed
information please see the
\href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information
for Authors}.

\subsection*{Author Affiliations}\label{author-affiliations}
\addcontentsline{toc}{subsection}{Author Affiliations}

Include department, institution, and complete address, with the
ZIP/postal code, for each author. Use lower case letters to match
authors with institutions, as shown in the example. Authors with an
ORCID ID may supply this information at submission.

\subsection*{Submitting Manuscripts}\label{submitting-manuscripts}
\addcontentsline{toc}{subsection}{Submitting Manuscripts}

All authors must submit their articles at
\href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you
are using Overleaf to write your article, you can use the ``Submit to
PNAS'' option in the top bar of the editor window.

\subsection*{Format}\label{format}
\addcontentsline{toc}{subsection}{Format}

Many authors find it useful to organize their manuscripts with the
following order of sections; Title, Author Affiliation, Keywords,
Abstract, Significance Statement, Results, Discussion, Materials and
methods, Acknowledgments, and References. Other orders and headings are
permitted.

\subsection*{Manuscript Length}\label{manuscript-length}
\addcontentsline{toc}{subsection}{Manuscript Length}

PNAS generally uses a two-column format averaging 67 characters,
including spaces, per line. The maximum length of a Direct Submission
research article is six pages and a PNAS PLUS research article is ten
pages including all text, spaces, and the number of characters displaced
by figures, tables, and equations. When submitting tables, figures,
and/or equations in addition to text, keep the text for your manuscript
under 39,000 characters (including spaces) for Direct Submissions and
72,000 characters (including spaces) for PNAS PLUS.

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g. (1) and (2, 3). All
references, including for the SI, should be included in the main
manuscript file. References appearing in both sections should not be
duplicated. SI references included in tables should be included with the
main reference section.

\subsection*{Data Archival}\label{data-archival}
\addcontentsline{toc}{subsection}{Data Archival}

PNAS must be able to archive the data essential to a published article.
Where such archiving is not possible, deposition of data in public
databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata,
and others outlined in the Information for Authors, is acceptable.

\subsection*{Language-Editing Services}\label{language-editing-services}
\addcontentsline{toc}{subsection}{Language-Editing Services}

Prior to submission, authors who believe their manuscripts would benefit
from professional editing are encouraged to use a language-editing
service (see list at www.pnas.org/site/authors/language-editing.xhtml).
PNAS does not take responsibility for or endorse these services, and
their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}
\centering
\includegraphics{frog.png}
\caption{Placeholder image of a frog with a long example caption to show
justification setting.{}}
\end{figure}

\subsection*{Digital Figures}\label{sec:figures}
\addcontentsline{toc}{subsection}{Digital Figures}

Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for
figures that will appear in the main text, and images must be final
size. Authors may submit U3D or PRC files for 3D images; these must be
accompanied by 2D representations in TIFF, EPS, or high-resolution PDF
format. Color images must be in RGB (red, green, blue) mode. Include the
font files for any text.

@@

\hypertarget{refs}{}
\hypertarget{ref-belkin2002using}{}
1. Belkin M, Niyogi P (2002) Using manifold stucture for partially
labeled classification. \emph{Advances in Neural Information Processing
Systems}, pp 929--936.

\hypertarget{ref-berard1994embedding}{}
2. Bérard P, Besson G, Gallot S (1994) Embedding riemannian manifolds by
their heat kernel. \emph{Geometric \& Functional Analysis GAFA}
4(4):373--398.

\hypertarget{ref-coifman2005geometric}{}
3. Coifman RR, et al. (2005) Geometric diffusions as a tool for harmonic
analysis and structure definition of data: Diffusion maps.
\emph{Proceedings of the National Academy of Sciences of the United
States of America} 102(21):7426--7431.

>>>>

\begin{abstract}
(Current count: 153) Valuation effects are consistently observed in
medial prefrontal and posterior cingulate cortex (mPFC and PCC). The
spatial extent of these effects is mostly indistinguishable from the
default mode network (DMN) in existing meta-analyses. However, little is
known about how valuation effects fit within the broader functional
architecture of mPFC and PCC, or whether that architecture is consistent
or idiosyncratic across individuals. Here we complement a meta-analysis
with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at
the single-subject level. Our results suggest the functional topography
of mPFC has substantial variability across individuals. This highlights
the potential usefulness of estimating brain effects at the individual
level in this region, and points to limitations of aggregative methods
such as coordinate-based meta-analysis in determining whether valuation
and DMN effects emerge from common or separable brain systems. Our
approach shows promise in addressing this issue through future
manipulations of valuation.
\end{abstract}

@@

(current, 676 words. Aim for 650)

The medial prefrontal cortex (mPFC) has been suggested to subserve many
of the cognitive abilities that differentiate humans from other animals
(Barbas \& Garcia-Cabezas, 2016). Specifically, this region has been
related to decision making (Bartra, McGuire, \& Kable, 2013), memory
encoding (Shacter, Addis, \& Buckner, 2007), and default mode
deactivation (DMN) (Yeo et al., 2011), among ohters. While much has been
discovered about this area in primates (Barbas \& Garcia-Cabezas, 2016),
the lack of direct measurements of neuronal activity makes this a tough
area to record in humans, one that nowadays relies mostly on functional
MRI (fMRI). Unfortunately, the mPFC is especially challenging to image,
as the oxygen-related signal recorded by fMRI is contaminated by the
oxygen in the sinuses (Logothetis, 2008). In addition, this area is
subject to more idiosyncratic cortical folding than any other region
(Zilles, Palomero- Gallagher, \& Amunts, 2013), thus adding a level of
complexity to the generalizable dissection of topographic functional
roles within mPFC.

Previous meta analytic studies have provided important insights on the
psychological phenomena attributed to mPFC subregions. For example, de
la Vega et al. (2016) found subdivisions of mPFC and MCC that are
significantly tied to decision making in the literature. In particular,
they show that more ventral regions are more tightly associated with
reward and fear. However, this pattern overlaps with their finding that
vmPFC also coactivates with DMN regions, and find no topographical
distinction between these phenomena. Similarly, the results from Bartra
et al and Laird et al show that this region can't be subdivided into DMN
vs subjective value (acikalin, chris, russ). However, meta analyses rely
on peaks often derived from group-averaged data. Recent work has
prescribed relevance to the analysis of single subjects in fMRI. Yeo et
al (2018) propose the use of individualized topologies when identifying
functional networks. Gordon et al identify important idiosincrasies in
oversampled subjects. Similarly, Braga and Buckner show that finer
subdivisions of the DMN are possible when looking at each subject
independently. This opens up the possibility that distinctions between
DMN and subjective value are possible at this finer level of resolution,
but would otherwise be masked in meta analytic work.

Braga \& Buckner's work is particularly informative when it comes to
subdividing DMN. However, the seed-based functional connectivity
analysis is sensitive to the selection of the seed. A natural next step
would be to recruit all possible patterns of covariation within this
network. A popular alternative is to rely on graph theoretic methods,
which provide a characterization of networks that organically fits brain
dynamics (provides an organic avenue to understand brain dynamics?), and
thus permits the consideration of the full covariance structure of brain
networks. (ADV \& Tal somewhere here).

Given the shortcomings of study-specific and cross-study analyses
mentioned above, there is potential value in combining complementary
strengths from both approaches. Focusing on resting state data has been
successful in determining a number of neural phenomena, including
disentangling auditory and visual attention areas (Tobyne, Osher,
Michalka, \& Somers, 2017).

One great advantage of network science is the ability to characterize
connectivity in a way that allows for comparisons among individuals in a
meaningful way (Garcia, Ashourvan, Muldoon, Vettel, \& Bassett, 2018),
thus letting us address the idiosyncrasies mentioned above. In this
study, we aim to subdivide mPFC into subject-specific DMN and non-DMN
areas, so that we can generate more informed topographic targets for
future studies of decision making. We address this aim at 3 levels of
granularity: 1) across the literature (meta-analysis), selecting a
number of regions of interest (ROI) that show significant overlap and
specificity between DMN and decision making; 2) full-brain connectivity
of actual fMRI data, using a pre-specified brain atlas; and 3)
characterizing the connectivity of surface vertices (small units of
function that contain oxygen-dependent neural information across time)
for the regions selected in step one. I performed the last two steps at
an individual subject level for 3 subjects, hoping to find some
commonalities among them. In this way, I attempted to extract functional
topographical information from topological network features.

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/Partition comparison: all brain example-1.pdf}
\caption{Template brain.}
\end{figure}

@@

(1500 words max)

@@

See \url{http://www.jneurosci.org/content/preparing-manuscript}

\textbf{Meta-analysis} To perform the first step, I used data from a
metanalysis that gathered peak brain coordinates of activity from
studies of valuation (n = 27 studies) and DMN (n = 77). These are the
surviving areas post-statistical thresholding from each study. I
analyzed this data by mapping the peak cortical coordinates to an atlas
of the human cortical surface (Glasser et al., 2016). This produced a
list of standardized parcels that were reported on each study. The
advantage of utilizing this atlas was threefold: first, it reduced the
number of functional vertices from 60,000 (cortical surface vertices) to
360 (cortical parcels). Second, it standardizes the vertices from the
first to the second stage of my study. Finally, it allowed me to project
each area on a brain space without much clutter. Since each vertex is
embedded with topographical information, and since functional topography
is essential to my question, I mostly project my results onto brain
space.

I thus generated two undirected, loop-less, weighted graphs in which
each vertex was a brain parcel, and edges correspond to the number of
times each pair of them co-occurred across studies. Since different
decision tasks use different sensory modalities, and since sensory areas
get sometimes reported as unrelated peak coordinates in DMN studies, I
bootstrapped the co- occurrences across studies and removed edges whose
co-occurrences lied below the 90th percentile. Based on this, only edges
with co-occurrences higher than 8 were preserved, and the remaining
unconnected vertices (brain regions) were discarded. With these graphs
set up, I computed the strength and betweenness centrality in order to
capture each parcel's centrality in the valuation and DMN literatures
separately.

In order to select of regions of interest (ROI) from mPFC and other
brain areas that are central to valuation and DMN literatures, I first
bootstrapped the mean strength for each graph separately, and chose
areas with strength above the 95th percentile of this distribution.
Next, I took the intersection of these areas, such that the final ROIs
were brain regions that overlapped between DMN and valuation in the
literature (and thus my main target for dissociation).

\textbf{Whole Brain Parcellated connectivity} For the second step, in
order to actually quantify the intrinsic connectivity of these ROIs in
the brain, I used data from the Human Connectome Project. Specifically,
I acquired resting-state fMRI activity from 3 subjects, all of whom have
been preprocessed according to industry standards to allow for
group-level comparisons (Tobyne et al., 2017). Each data set contained
around 1 hour of signals represented as 4800 time points, and each
subject contained 60,000 vertices. I parcellated each subject's brain
according to the atlas mentioned above, so that each parcel contained
the mean time series from its vertices, and correlated the mean time
series among all parcels (Pearson). This produced a weighted adjacency
matrix for each subject, where each of the 360 parcels is a vertex, and
edges the correlations among all of them. Next, I took the exponential
of the correlations, Fisher transformed them (i.e.~tanh) so that all
weights were positive while maintaining the shape of the original
correlation distribution, and retained the edges whose adjusted p-values
remained significant (FDR \textless{} 0.05). Again, I quantified each
parcel's strength and betweenness, averaged them across subjects, and
examined whether any of the ROIs showed uniquely high centralities. For
this, I performed a permutation comparing the mean strength between the
ROIs and the rest of the brain for each participant.

For the main goal of this section, I maximized the strength-based
modularity metric as a community detection method (fast-greedy
algorithm), so that I could check if all the DMN ROIs from the previous
section were affiliated with the same community. While this measure has
resolution problems at large and low scales (Fortunato \& Hric, 2016),
if it does extract a close match to standard DMN networks, it could act
as a good method for the final stage of the project (but see Peel,
Larremore, and Clauset 2017 for issues with ground-truth). Even though
this analysis is mainly geared to confirm that these ROIs are jointly
captured, this step also let me examine whether some of the ROIs could
be subdivided into DMN and non-DMN regions at this level of granularity.

In order to evaluate the validity of the modularity-based communities, I
also clustered the brain by means of spectral partitioning.
Specifically, I took the Fiedler vector (eigenvector associated with the
second lowest eigenvalue) from each participant's normalized Laplacian
matrix, and divided the brain by the sign of the eigenvector values.
This analysis served the additional purpose of more strictly dividing
the brain into DMN and non-DMN communities. Importantly, given the high
density of these networks (see results), spectral partitioning was
unlikely to face the issues associated with its use in sparse networks
(Fortunato \& Hric, 2016). Finally, to quantify the agreement of these
community methods, I computed both the adjusted rand index and variation
of information distance (normalized by the logarithm of the number of
vertices, 360 in this case) between them per subject. The adjusted rand
index denotes the proportion of vertices that coincide in affiliation
across partitions, and compares this score to a baseline given by the
expectation based on a random vertex assignment for an equal number of
clusters across partitions. On the other hand, variation of information
gives a general sense of the amount of information to be gained by the
complementary community partitioning (Meila, 2007), measured by the
addition of the conditional entropies per combination of clusters across
partitions. While the rand index is more easily interpreted, it suffers
from the assumption that the baseline should have an equal number of
vertices per cluster across partitions, which is not necessarily the
case. Therefore, I used variation of information as a more robust
similarity metric (Fortunato \& Hric, 2016). Importantly, due to having
just 3 subjects, I abstained from performing formal statistics on the
descriptive measures that I show.

\textbf{Within-ROI Connectivity} For the third stage, I ``zoomed in''
each subject's brain by computing the correlation among all of the
surface-vertices contained within each ROI across all the ROIs, and
applied the same correction as in step two. That means that the vertices
became smaller functional brain units that are connected by the same
type of edge (i.e.~adjusted correlations) as in step two. This time, I
only focused on partitioning the brain through modularity and spectral
partitioning to see if the ROIs can be subdivided at this finer level of
resolution. It is worth noting that while communities across subjects
should be similar, the idiosyncrasies explained previously
(i.e.~cortical folding) should produce noticeable differences as well.

This time I added two new areas to the ROIs: 7m, as this area had unique
relevance in DMN when compared to valuation (evidenced by its
connectivity strength in DMN and chi- squared permutation in the
meta-analysis, see results), and V1, as this visual processing area
should not be affiliated with DMN. These regions thus acted as dual
reference points, such that the community affiliated with 7m should
denote DMN, while V1 indicated non-DMN. As before, I tested the validity
of the partitions using the adjusted rand index and normalized variation
of information. However, this time I also used the rand index to
quantify the community correspondence between subjects. Specifically, I
divided each subject's spectrally- partitioned brain into PCC and mPFC
topographical zones (posterior and frontal brain, respectively), and
computed the index of each region between subjects. The high
cross-subject heterogeneity of cortical folding of mPFC should produce
relatively low rand indices, while the more homogeneous PCC should
display the opposite pattern. This analysis was meant to tackle the
subject-specific limitations discussed above. The final patterns were
inspected visually.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

@@
